Perturbing SU($n$)-symmetric interactions

### 2019-10-30 collective_sun/sun_perturbation.tex
fixed minor errors

$\tilde h_{k\ell} v_{k\ell}$; $\m h\c\m v$ denotes an ordinary matrix

@@

where $v\equiv\sum_{p<q}v_{pq}/N$ is the mean value of the

@@

The two-body case requires a bit of work to re-cast as an
eigenvector/eigenvalue problem.  We first write the matrix $\m v$ as a
vector,
\begin{align}
  \m v = \sum_{k,\ell} v_{k\ell} \op{k}{\ell}
  \to \v{\m v} \equiv \sum_{k,\ell} v_{k\ell} \ket{k\ell},
\end{align}
and define the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{k,\ell} \bar h_{k\ell} \op{k\ell}
  + \sum_{k,q,\ell} h_{kq} \op{k\ell}{q\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:v_cond_2} becomes
\begin{align}
  \check{\m h} \c \v{\m v} = \e\p{\m v} \v{\m v}.
\end{align}
Note that the matrix $\check{\m h}$ in \eqref{eq:h_super_mat} can be
written in the block-diagonal form
\begin{align}
  \check{\m h} = \sum_\ell \m h_\ell \otimes \op{\ell},
  &&
  \m h_\ell
  \equiv \sum_{k,q}\p{\delta_{kq} \bar h_{k\ell} + h_{kq}} \op{k}{q},
\end{align}
where each block $\m h_\ell$ is an $N\times N$ matrix.  We can
diagonalize these blocks independently, and classify their
eigenvectors by the corresponding eigenvalues.  ``Total'' eigenvectors
$\v{\m v}$ of $\check{\m h}$ are then essentially built from
eigenvectors within each block $\m h_\ell$ that share the same
eigenvalue.  The task of constructing eigenvectors
$\V_2\p{\m v}\ket\psi$ of $H_0$ and determining their energy thus
reduces to finding the eigenvectors and eigenvalues of $N$ matrices
$\m h_\ell$ of size $N\times N$.

>>>>

$\bar h_{k\ell} v_{k\ell}$; $\m h\c\m v$ denotes an ordinary matrix

@@

where $v\equiv\sum_{p<q}v_{pq}/N$ is the mean value of the pair-wise

@@

In order to re-cast the two-body condition in \eqref{eq:v_cond_1} as
an eigenvector/eigenvalue problem, we write the matrix $\m v$ as a
vector,
\begin{align}
  \m v = \sum_{k,\ell} v_{k\ell} \op{k}{\ell}
  \to \v{\m v} \equiv \sum_{k,\ell} v_{k\ell} \ket{k\ell},
\end{align}
and define the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{k,\ell} \bar h_{k\ell} \op{k\ell}
  + \sum_{k,q,\ell} h_{kq} \op{k\ell}{q\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:v_cond_2} becomes
\begin{align}
  \check{\m h} \c \v{\m v} = \e\p{\m v} \v{\m v}.
\end{align}
Note that the matrix $\check{\m h}$ in \eqref{eq:h_super_mat} can be
written in the block-diagonal form
\begin{align}
  \check{\m h} = \sum_\ell \m h_\ell \otimes \op{\ell},
  &&
  \m h_\ell
  \equiv \sum_{k,q}\p{\delta_{kq} \bar h_{k\ell} + h_{kq}} \op{k}{q},
\end{align}
where each block $\m h_\ell$ is an $N\times N$ matrix.  We can
diagonalize these blocks independently, and classify their
eigenvectors by the corresponding eigenvalues.  ``Total'' eigenvectors
$\v{\m v}$ of $\check{\m h}$ are then essentially built from
eigenvectors within each block $\m h_\ell$ that share the same
eigenvalue.  The task of constructing eigenvectors
$\V_2\p{\m v}\ket\psi$ of $H_0$ and determining their energy thus
reduces to finding the eigenvectors and eigenvalues of $N$ matrices
$\m h_\ell$ of size $N\times N$.
